\documentclass[11pt, letterpaper]{article}
\usepackage[utf8]{inputenc}

\title{SFWRENG 3XA3: Problem Statement}
\author{Team L03G09 \\
		Longwei Ye(yel16) \\
		Qiang Gao(gaoq20) \\
		Zhiwei Li(liz342) \\}
\date{\today}

\begin{document}

\begin{titlepage}
\maketitle
\end{titlepage}


\section*{Problem that needed to be addressed}
Gaming on a computer is a convenient and effective way for people's daily entertainment, especially 
when people are trying to relax themselves. We, as the game developers, are trying to provide a satisfying 
gaming experience for the users by ensuring the quality of the in-game graphic interface as well as the playability 
of the game itself. The game we are trying to modify is already a classic game. However, we are modifying 
the project with a modernized and attractive user interface and an enhanced in-game mechanic so that the game 
can keep track of the latest trends.

\section*{The importance of the problem}
Game interface design is very important for games, as it ties every part of the game together smoothly and makes users 
get more enjoyment out of it. A user-friendly game interface design will make the user enjoy the game and quickly immerse 
him or her in the game. Also, the user interface of a game usually gives users the very first impression. 
Sometimes, even an eye-catching logo is able to attract loads of users to try the game. \\

\noindent The mechanics or the rules are the key of a game. Clever mechanics can give a game enduring appeal. 
This is why the chess game can be popular for centuries. Therefore, based on the original game, we want to add 
more interesting modes or tools to make it more playable.

\section*{Context of the problem}
The majority stakeholders of this project are gamers who enjoy the single-player mode for self challenging or two-player mode 
sharing with their friends. \\

\noindent Based on the programming language Javascript together with CSS and HTML, the game is designed to run on a computer
where a browser is implemented, which is a basic and general environment for nowadays main-stream desktop and mobile devices. \\

\noindent To help users and future developers to get a clear overview of the project, we will implement the improvement with 
associated documentation, as new guidance from the original project. 

\end{document}